### 2016-07-12 R/ITHIM.Rmd
Continued to work on MET distribution

summaryList$metaData <- within(summaryList$metaData,{
    AGECAT <- ifelse(TEAGE <5, "age0-4",
                     ifelse(TEAGE > 4 & TEAGE < 15, "age5-14",
                     ifelse(TEAGE > 14 & TEAGE < 30, "age15-29",
                     ifelse(TEAGE > 29 & TEAGE < 45, "age30-44",
                     ifelse(TEAGE > 44 & TEAGE < 60, "age45-59",
                     ifelse(TEAGE > 59 & TEAGE < 70, "age60-69",
                     ifelse(TEAGE > 69 & TEAGE < 80, "age70-79", "age80+"
                            )))))))})

@@

```{r metKey}
metKeyVector <- metKey[activities]/60*7
names(metKeyVector) <- activities
metKeyMatrix <- matrix(metKeyVector, nrow = nrow(summaryList$Data), ncol = length(metKeyVector), byrow = TRUE)

@@

```{r dists}
D <- merge(cps, METs, by.y = "row.names", by.x = "TUCASEID")
ggplot(D, aes(x = METs, ..density.., colour = AGECAT)) + geom_freqpoly() + facet_grid( SEX ~ GEREG )
```

>>>>

summaryList$metaData <- within(summaryList$metaData,{
    TESEX <- as.factor(TESEX)
    AGECAT <- ifelse(TEAGE <5, "age0-4",
                     ifelse(TEAGE > 4 & TEAGE < 15, "age5-14",
                     ifelse(TEAGE > 14 & TEAGE < 30, "age15-29",
                     ifelse(TEAGE > 29 & TEAGE < 45, "age30-44",
                     ifelse(TEAGE > 44 & TEAGE < 60, "age45-59",
                     ifelse(TEAGE > 59 & TEAGE < 70, "age60-69",
                     ifelse(TEAGE > 69 & TEAGE < 80, "age70-79", "age80+"
                            )))))))})

@@

```{r metKey}
metKeyVector <- (metKey[activities] - min(metKey, na.rm = TRUE))/60*7
names(metKeyVector) <- activities
metKeyMatrix <- matrix(metKeyVector, nrow = nrow(summaryList$Data), ncol = length(metKeyVector), byrow = TRUE)

@@

D <- merge(cps, METs, by.y = "row.names", by.x = "TUCASEID")
ggplot(D, aes(x = METs, ..density.., colour = AGECAT)) + geom_freqpoly() + facet_grid( SEX ~ .)
#ggplot(D, aes(x = METs, ..density.., colour = SEX)) + geom_freqpoly()
```

```{r paameters}
parameters <- ddply(D, .(SEX), summarise,
             mean = mean(METs, na.rm=T),
             sd = sd(METs, na.rm=T)
             )
```
